TAPIR: Threaded Application Programming on Intermittent Resources

### 2017-05-10 paper.tex

\section{Introduction/Background} -Amanda
  \label{sec:intro}
  Chain, DINO\\
  Multithreading\\
  Intermittence Review\\
  RMW\\
  Example Citation\cite{Chain, Mementos, Aware, Dino}!

@@

\section{Future Work} -Amanda
Duplicating channels (a little renaming or sharing arrays with mutexes)\\
Optimizations to reduce overhead\\

>>>>

\section{Introduction/Background} -Amanda
  \label{sec:intro}
  Chain, DINO\\
  Multithreading\\
  Intermittance Review\\
  RMW\\
  Example Citation\cite{Chain, Mementos, Aware, Dino}!

@@

\section{Future Work} -Amanda
Duplicating channels (a little renaming or sharing arrays with mutexes)\\
Optimizations to reduce overhead\\
\\
Automatically renaming channels to reuse task code\\
-challenging to define sharing between threads\\
-challenging to constrain memory for channels (not that much of it, also compilation)\\
-challenge to uniquely identify multiple channel instances of the same task\\
\\
Optimizations to reduce overhead\\
-convert free indices array to bitmap\\
-compile-time re-assignation of re-used channels\\
